---
title: 'Analyzing Happy Moments: Where Does Happiness Come From?'
author: "WENHE CHEN"
---

```{r warning=FALSE, echo=FALSE}

options(repos = c(CRAN = "https://cloud.r-project.org"))
install.packages("RColorBrewer")
install.packages("lmerTest")
install.packages(c("tidyverse", "tm", "textdata", "topicmodels", "wordcloud", "syuzhet"))
install.packages("plotly")
library(plotly)
library(ggplot2)
library(dplyr)
library(wordcloud)
library(tidyverse)
library(tidyr)
library(conflicted)



```

# Introduction

In this fast-paced era, everyone wants to pursue their happiness. However, everyone may give a different answer to what happiness is. Analyzing the happiness life gives us and unlocking the proper sources of happiness is the goal of this exploration.

Although happiness is a human state of feeling, a complex mixture of factors that cannot be seen or touched by positive emotions, we will open the door to a new world through human words and data analysis. Here, we can glimpse the true nature of happy moments and draw inspiration from data science and text analytics.

The HappyDB dataset will be at the heart of this project. This dataset is a treasure trove of information that contains five files:

cleaned_hm.csv: This file is an enhanced version of original_hm.csv and provides a clean version of happy moments, including reflection cycles, person IDs, and sentences that express happiness

original_hm.csv: This file is an unfiltered moment of joy and preserves the original

Demograph.csv: This file delves into demographic details such as age, gender, and location

senselabel.csv: This file is an annotated version of the cleaned-up Happy Moments and provides insights into various lexical aspects, including parts of speech tags and hyper meaning tags

topic_dict/*-dict.csv: This file provides classification views


# Data Exploration and Reflection Period Analysis


The cleaned data is enormous and can also provide us with more accurate data. People's responses to happiness can reflect all kinds of information. In a survey of more than 100,000 people, 49,831 chose to review a happy moment within 24 hours, and 50,704 chose to review a happy moment within three months. Overall, many people choose to look back on a happy moment within three months. This data may suggest that people are more likely to spot moments of happiness in the long run. In other words, people need to compare their historical state with their present state to find out whether they are in a happy state, but it is not significant.


```{r warning=FALSE, echo=FALSE}
cleaned_hm <- read.csv("cleaned_hm.csv")

cleaned_hm_clean <- cleaned_hm %>% dplyr::filter(!is.na(cleaned_hm))

summary(cleaned_hm_clean)
```
```{r warning=FALSE, echo=FALSE}

reflection_analysis <- cleaned_hm_clean %>% 
  group_by(reflection_period) %>% 
  summarise(count = n())

ggplot(reflection_analysis, aes(x = reflection_period, y = count)) +
  geom_bar(stat = "identity", aes(fill = reflection_period)) +
  geom_text(aes(label = count), vjust = -0.5) +
  theme_minimal() +
  labs(title = "Reflection Period Analysis", 
       x = "Reflection Period", 
       y = "Count")
```

# The Source of Happy Emotions

According to the research on the label of happiness description, the external environment influences whether people feel happy. Around 68,000 of those happy moments came from affection or achievement, making them the top two sources of happiness. Hence, affection and achievement have an essential place in the well-being of most people. However, only 3,045 people reported happy moments related to nature or exercise. Overall, the data suggest that people are more focused on the happiness of relationships or personal achievements in their lives.

```{r warning=FALSE, echo=FALSE}
category_analysis <- cleaned_hm_clean %>%
  group_by(predicted_category) %>%
  summarise(count = n())


plot_ly(category_analysis, x = ~reorder(predicted_category, -count), y = ~count, type = 'bar') %>%
  plotly::layout(title = "Predicted Category Distribution",
                 xaxis = list(title = 'Predicted Category'),
                 yaxis = list(title = 'Count'))

```


Affection and achievement are two expansive themes. In order to find out exactly where happy moments originate, we need to explore further.

The most frequent word was "date" after accumulating high-frequency words from the sentence that described happy moments. The rest are "felt," "someone," "successful," "went," "got," and "happy." As a result, the interpretation of each word suggests that people are likelier to have their happiest moments on a dating or special day. In addition, family and friends will also feel happy when they get together. This result aligns with the previous label belonging to the affection category.

In addition, high-frequency words in repetitive categories were removed, such as "happy," "time," today," day," "good," and "get." We can roughly divide high-frequency words into five categories. According to the analysis, five categories can be defined as new experiences and social, work and time experiences, family celebrations and discoveries, daily life and close relationships, and positive personal experiences. As a result, when people describe happy moments, they often first mention interactions and social activities with relatives and friends. Secondly, the novelty brought by people's exploration of new things or achievements in work will stimulate people's perception of the outside world, thus improving their happiness. In other words, people feel delighted when satisfied with the present situation.

In summary, when describing happy moments, people tend to focus on aspects of social interactions, new experiences, daily life and work, and aspects of time, memories, and emotions. This consequence indicates the diversity of people's sources of happiness.

```{r warning=FALSE, echo=FALSE}
library(tm)
library(textdata)

cleaned_hm_clean$cleaned_hm <- iconv(cleaned_hm_clean$cleaned_hm, to = "UTF-8", sub = "")

# 文本预处理
corpus <- Corpus(VectorSource(cleaned_hm_clean$cleaned_hm))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, stopwords("en"))


dtm <- DocumentTermMatrix(corpus)

# 找出最常出现的词
most_common_words <- findFreqTerms(dtm, lowfreq = 100)

# 打印最常出现的词

head(most_common_words,30)

# 添加自定义去除词
my_stopwords <- c("happy", "time", "went", "got", "made", "today","really","finally","day","good","get")
corpus <- tm_map(corpus, removeWords, my_stopwords)

# 删除
dtm <- DocumentTermMatrix(corpus)
dtm <- removeSparseTerms(dtm, 0.99)

# 检查是否还有空文档
row_sums <- rowSums(as.matrix(dtm))
if(any(row_sums == 0)) {
  dtm <- dtm[row_sums > 0, ]
}

install.packages("topicmodels")

library(topicmodels)

# LDA模型
lda_model <- LDA(dtm, k = 5, control = list(seed = 1234))

# 查看前几个主题的前几个关键词
terms(lda_model, 10)
```
```{r warning=FALSE, echo=FALSE}
library(tidytext)
tidy_lda <- tidy(lda_model)
top_terms <- tidy_lda %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered()

```

# Sentiment Analysis

After sentiment analysis of more than 100,000 sentences, the data showed that joy and positive emotions scored higher on average than others. It also means that people are more likely to use words with positive emotions to describe happy moments, and it makes sense. At the same time, the average score of trust and anticipation is also high. This circumstance may indicate that people also tend to experience a certain level of trust during happy moments, and a mood of anticipation often accompanies that happy moment. Therefore, when people describe happiness, they may not describe just a moment but a process. Moreover, people may experience happiness and satisfaction in the process.

Surprisingly, however, the people surveyed could use negative words such as anger or disgust to express or describe happy moments. Thus, it may be suggested that when describing a happy moment, people may also refer to emotions that are opposite or different from that moment to emphasize its uniqueness or value. Alternatively, people associate other background information with different emotions when describing a happy moment. In short, people experience happiness and describe happy moments in diverse and complex ways.

```{r warning=FALSE, echo=FALSE}
library(syuzhet)

batch_size <- 1000
n <- nrow(cleaned_hm_clean)
n_batches <- ceiling(n / batch_size)

sentiments <- data.frame()

for(i in 1:n_batches) {
  start_index <- ((i - 1) * batch_size) + 1
  end_index <- min(i * batch_size, n)
  
  batch <- cleaned_hm_clean[start_index:end_index, ]
  batch_sentiments <- get_nrc_sentiment(as.character(batch$cleaned_hm))
  sentiments <- rbind(sentiments, batch_sentiments)
  
  print(paste("Processed batch", i, "of", n_batches))
}

```


```{r warning=FALSE, echo=FALSE}
summary(sentiments)
```

```{r warning=FALSE, echo=FALSE}
library(ggplot2)


sentiments_summary <- colMeans(sentiments[sapply(sentiments, is.numeric)], na.rm = TRUE)




sentiments_summary_df <- data.frame(
  sentiment = names(sentiments_summary),
  score = as.numeric(sentiments_summary)
)



ggplot(sentiments_summary_df, aes(x = sentiment, y = score)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  coord_flip() + 
  ggtitle("Average Score for Each Sentiment") +
  xlab("Sentiment") +
  ylab("Average Score")

```

# The interrelationship of sources of happiness


Age, gender, or nationality could influence the source of our perceived happiness moments. Across the board, different age groups used roughly the same number of sentences to describe happy moments. Thus, there was no significant difference between the age group and the average number of sentences used to describe happy moments. Nevertheless, from a comparative point of view, people aged 21 to 30 were more likely to use more sentences to describe their happy moments. People in this age group are young; they may be full of aspirations for the future and, therefore, more willing to share and express their current feelings and experiences, or it may mean that they have more time and social activities to share their happy moments. In addition, although the number of sentences people used to describe happy moments did not decrease significantly with age, the number of happy moments people shared gradually decreased with age, which may mean that older people enter a state of polarization between being willing to share actively and being less willing to share.


According to the analysis of gender and number of happy moments, men were counted far more than women. The result could mean that men in the survey area have more time on their hands, are more likely to share their happy moments through social events or on the platform, or there are more male users. The analysis of the region of nationality and the number of happy moments offers few conclusions. This data only shows that the most happy moments were shared in the USA, which may be because the majority of the survey or platform population is in the USA.

```{r warning=FALSE, echo=FALSE}

demographic_data <- read.csv("./demographic.csv")
cleaned_hm_data <- read.csv("./cleaned_hm.csv")

merged_data <- merge(demographic_data, cleaned_hm_data, by = "wid")


merged_data$age <- as.numeric(as.character(merged_data$age))


merged_data <- merged_data %>% mutate(age_group = cut(age, 
                                                      breaks = c(0, 20, 30, 40, 50, 60, 100), 
                                                      labels = c("0-20", "21-30", "31-40", "41-50", "51-60", "60+"),
                                                      include.lowest = TRUE))

age_group_analysis <- merged_data %>% 
  group_by(age_group) %>% 
  summarise(avg_num_sentence = mean(num_sentence, na.rm = TRUE))

print(age_group_analysis)


ggplot(age_group_analysis, aes(x = age_group, y = avg_num_sentence, fill=age_group)) + 
  geom_bar(stat = "identity") + 
  xlab("Age Group") + 
  ylab("Average Number of Sentences") + 
  ggtitle("Average Number of Sentences in Happy Moments by Age Group")


```


```{r warning=FALSE, echo=FALSE}

#read csv files
demographic_data <- read.csv("demographic.csv")
cleaned_hm_data <- read.csv("cleaned_hm.csv")


merged_data <- merge(demographic_data, cleaned_hm_data, by = "wid")

#creat age group
merged_data <- merged_data %>%
  mutate(
    age_group = case_when(
      age <= 20 ~ "Under 20",
      age > 20 & age < 31 ~ "20-29",
      age >= 31 & age < 41 ~ "30-39",
      age >= 41 & age < 51 ~ "40-49",
      age >= 51 & age < 61 ~ "50-59",
      TRUE ~ "61 and above"
    )
  )

#age
age_analysis <- merged_data %>%
  group_by(age_group) %>%
  summarize(
    happy_moments = list(original_hm),
    n = n(),
    .groups = 'drop'
  )

#gender
gender_analysis <- merged_data %>%
  group_by(gender) %>%
  summarize(
    happy_moments = list(original_hm),
    n = n(),
    .groups = 'drop'
  )

#country
country_analysis <- merged_data %>%
  group_by(country) %>%
  summarize(
    happy_moments = list(original_hm),
    n = n(),
    .groups = 'drop'
  )

```


```{r warning=FALSE, echo=FALSE}
ggplot(age_analysis, aes(x = age_group, y = n, fill=age_group)) + 
  geom_bar(stat = "identity") + 
  xlab("Age Group") + 
  ylab("Number of Happy Moments") + 
  ggtitle("Number of Happy Moments by Age Group")
```


```{r warning=FALSE, echo=FALSE}
ggplot(data = gender_analysis, aes(x = gender, y = n, fill = gender)) +
  geom_bar(stat = "identity") +
  xlab("Gender") +
  ylab("Happy Moment Count") +
  ggtitle("Happiness Analysis by Gender")

```
```{r warning=FALSE, echo=FALSE}

country_analysis <- country_analysis %>%
  arrange(desc(n))

print(country_analysis)
print(gender_analysis)
print(age_analysis)
```




```{r warning=FALSE, echo=FALSE}
cleaned_hm <- read.csv("cleaned_hm.csv")
senselabel<- read.csv("senselabel.csv")


merged_senselabel <- merge(cleaned_hm, senselabel, by = "hmid")


multi_word_expression <- merged_senselabel %>% 
  dplyr::filter(MWE != 'O') %>%
  group_by(word) %>%
  summarise(count = n())


wordcloud(words = multi_word_expression$word, freq = multi_word_expression$count, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"))


super_sense_label <- merged_senselabel %>% 
  dplyr::filter(!is.na(supersenseLabel)) %>%
  group_by(supersenseLabel) %>%
  summarise(count = n())


wordcloud(words = super_sense_label$supersenseLabel, freq = super_sense_label$count, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"))


```

# Summary

People's sources of happiness are complex, and each person's sources of happiness are unique. In simple terms, the sources of people's happiness moments are more likely to be social interactions and sports, new experiences, the sense of accomplishment, emotion, ownership, and cognition brought by daily life and family. All kinds of people and things affect where happiness comes from and how it is experienced.


# References

Akari Asai, Sara Evensen, Behzad Golshan, Alon Halevy, Vivian Li, Andrei Lopatenko, 
Daniela Stepanov, Yoshihiko Suhara, Wang-Chiew Tan, Yinzhan Xu, 
``HappyDB: A Corpus of 100,000 Crowdsourced Happy Moments'', LREC '18, May 2018. (to appear)





